Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-07-11 paper/paper.tex
Added some questions to Sec 4

Figure \ref{fig:tree} shows as an illustration the results for a
single classification tree.  
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
The split in two classes is not perfect. 
This means that the 3 parameters in the
model are the most influential in finding models with low
$\chi^2/d.o.f.$, but that some combinations of the other 11 parameters
are also relevant to find a good fit.

@@

The best models are shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2/d.o.f.$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.

>>>>

Figure \ref{fig:tree} shows as an illustration the results for a
single classification tree.
\mg{Sorry but it is not clear to me what this Figure shows \& how it was assembled. I suggest: leave the KS test in the main text as it is straightforward to understand, and move the random trees with more technical details / references about the implementations to the appendix -- and then point to it as a second probe from the main tetx. This way it would break the flow less.}
The tree starts with $28$ and $1962$ models in the low and high
$\chi^2/d.o.f.$ classes, respectively. 
We find that the best classification
yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
The split in two classes is not perfect. 
This means that the 3 parameters in the
model are the most influential in finding models with low
$\chi^2/d.o.f.$, but that some combinations of the other 11 parameters
are also relevant to find a good fit.

@@

The best models are shown in Figure \ref{multiphaseresults}.
Left column shows the difference between the integrated distributions
of the full sample (2500 input models) and the models with the lowest
$\chi^2/d.o.f.$. 
The right column shows the actual $\chi^2/d.o.f.$ 
and its corresponding parameter value. 
Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
